---
title: "Untitled"
author: "Mingwen Yang"
date: "4/26/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


## Load data & Unit Root Test

```{r}
library(vars)
library(quantmod)
library(parallel)
library(rugarch)
library(rmgarch)
library(tseries)
library(zoo)
library(forecast)
library(fGarch)
library(FinTS)
library(lmtest)
library(urca)
library(xts)
library(Metrics)
library(DistributionUtils)
library(readxl)
library(fUnitRoots)
```
```{r}
ratedata = read.csv("D:/2019-2020/Time Series/hw/group/rate.csv")
rate = xts(ratedata$currency.rate, as.Date(ratedata$ï..DATE, format='%m/%d/%y', tz = "US"))
rate_train = rate[1:1080]
rate_test = rate[1081:1343]
#head(rate_train)
#tail(rate_train)
#head(rate_test)
#tail(rate_test)

df = read.csv("D:/2019-2020/Time Series/hw/group/data.csv")
data = ts(df[2:10], start = c(2015, 1), end = c(2020, 2), frequency=12)
head(data)
M1_US_rt = dailyReturn(data[, 1])
M1_EU_rt = dailyReturn(data[, 2])
GDP_US_rt = dailyReturn(data[, 3])
GDP_EU_rt = dailyReturn(data[, 4])
CPI_US_rt = dailyReturn(data[, 5])
CPI_EU_rt = dailyReturn(data[, 6])
XAU_USD_rt = dailyReturn(data[, 7])
WTI_USD_rt = dailyReturn(data[, 8])
RATE_rt = dailyReturn(data[, 9])

df_US = read_excel("D:/2019-2020/Time Series/hw/group/US_part.xlsx", sheet=1, na="NA")
data_US = ts(df_US[2:4], start = c(2011, 1), end = c(2020, 2), frequency = 12)
#head(data_US)
M1_US1_rt = dailyReturn(data_US[, 1])
CPI_US1_rt = dailyReturn(data_US[, 2])
RATE1_rt = dailyReturn(data_US[, 3])

df_D = read_excel("D:/2019-2020/Time Series/hw/group/DAILY_part.xlsx", sheet=1, na="NA")
data_D = xts(df_D[, 2:4], as.Date(df_D$DATE, format='%m/%d/%y', tz = "US"))
#head(data_D)
XAU_USD1_rt = dailyReturn(data_D$XAU_USD, type = "log")
WTI_USD1_rt = dailyReturn(data_D$WTI_USD, type = "log")
RATE2_rt = dailyReturn(data_D$`currency rate`, type = "log")
```
```{r}
adfTest(M1_US_rt)
adfTest(M1_EU_rt)
adfTest(GDP_US_rt)
adfTest(GDP_EU_rt)
adfTest(CPI_US_rt)
adfTest(CPI_EU_rt)
adfTest(XAU_USD_rt)
adfTest(WTI_USD_rt)
adfTest(RATE_rt)

GDP_EU_sta = ur.df(GDP_EU_rt, type='none', selectlags='AIC')
summary(GDP_EU_sta)
acf(GDP_EU_rt)
pacf(GDP_EU_rt)
GDP_EU_rt_dif = diff(GDP_EU_rt, 1)
adfTest(GDP_EU_rt_dif)
acf(GDP_EU_rt_dif, na.action = na.pass)
pacf(GDP_EU_rt_dif, na.action = na.pass)

GDP_EU_rt_dif[1] = 0
data_rt = cbind(M1_US_rt, M1_EU_rt, GDP_US_rt, GDP_EU_rt_dif, CPI_US_rt, CPI_EU_rt, XAU_USD_rt, WTI_USD_rt, RATE_rt)
names(data_rt) = c("M1_US", "M1_EU", "GDP_US", "GDP_EU", "CPI_US", "CPI_EU", "XAU_USD", "WTI_USD", "RATE")
head(data_rt)

data_rt_train = data_rt[1:50]
data_rt_test = data_rt[51:62]
head(data_rt_train)
tail(data_rt_train)
head(data_rt_test)
tail(data_rt_test)


adfTest(M1_US1_rt)
adfTest(CPI_US1_rt)
adfTest(RATE1_rt)

data_US_rt = cbind(M1_US1_rt, CPI_US1_rt, RATE1_rt)
names(data_US_rt) = c("M1", "CPI", "RATE")
#head(data_US_rt)
plot(as.xts(data_US_rt), type="l", multi.panel=TRUE, theme="white", main="M1_US & CPI_US & RATE", major.ticks="years", rid.ticks.on = "years")


adfTest(XAU_USD1_rt)
adfTest(WTI_USD1_rt)
adfTest(RATE2_rt)

data_D_rt = data.frame(XAU_USD1_rt, WTI_USD1_rt, RATE2_rt)
names(data_D_rt) = c("XAU", "WTI", "RATE")
#head(data_D_rt)
plot(as.xts(data_D_rt), type="l", multi.panel=TRUE, theme="white", main="XAU_USD & WTI_USD & RATE", major.ticks="years", rid.ticks.on = "years")

data_D_rt_train = data_D_rt[1:1330,]
data_D_rt_test = data_D_rt[1331:1344,]
```


## ARIMA & GARCH

Use "auto.arima" to fit a model for daily return of currency rate.  
Then check out ARCH effect to build GARCH model.
```{r}
md_arima_1 = auto.arima(rate_train)
md_arima_1
rate_train_rt = dailyReturn(rate_train, type = "log")
rate_test_rt = dailyReturn(rate_test, type = "log")
adfTest(rate_train_rt)
acf(rate_train_rt)
pacf(rate_train_rt)
```
```{r}
md_arima_2 = auto.arima(rate_train_rt)
md_arima_2
pred_arima = predict(md_arima_2, 263)
rmse(predicted = as.numeric(unlist(pred_arima[1])), actual = as.numeric(unlist(rate_test_rt)))
```

```{r}
Box.test(md_arima_2$residuals^2, 10, type = "Ljung")
pacf(md_arima_2$residuals^2)
```

```{r}
md_arch_G = garchFit(~garch(1, 0), data = rate_train_rt, trace = F)
summary(md_arch_G)
pred_arch_G = predict(md_arch_G, 263)
pred_arch_G
rmse(predicted = as.numeric(unlist(pred_arch_G[1])), actual = as.numeric(unlist(rate_test_rt)))
```

```{r}
md_arch_t = garchFit(~garch(1, 0), data = rate_train_rt, cond.dist = c("std"), trace = F)
summary(md_arch_t)
pred_arch_t = predict(md_arch_t, 263)
pred_arch_t[1]
rmse(predicted = as.numeric(unlist(pred_arch_t[1])), actual = as.numeric(unlist(rate_test_rt)))
```

```{r}
md_garch_G = garchFit(~garch(1, 1), data = rate_train_rt, trace = F)
summary(md_garch_G)
pred_garch_G = predict(md_garch_G, 263)
rmse(predicted = as.numeric(unlist(pred_garch_G[1])), actual = as.numeric(unlist(rate_test_rt)))
```

```{r}
md_garch_t = garchFit(~garch(1, 1), data = rate_train_rt, cond.dist = c("std"), trace = F)
summary(md_garch_t)
pred_garch_t = predict(md_garch_t, 263)
rmse(predicted = as.numeric(unlist(pred_garch_t[1])), actual = as.numeric(unlist(rate_test_rt)))
```

```{r TGARCH}
md_tgarch = garchFit(~aparch(1,1), rate_train_rt, delta = 2, include.delta = F, trace = F)
summary(md_tgarch)
pred_tgarch = predict(md_tgarch, 263)
rmse(predicted = as.numeric(unlist(pred_tgarch[1])), actual = as.numeric(unlist(rate_test_rt)))
```


## VAR & VEC

```{r}
#Apply granger test for determining whether one time series is useful in forecasting currency rate.
grangertest(M1_US_rt, RATE_rt, order = 1, na.action = na.omit)
grangertest(M1_EU_rt, RATE_rt, order = 1, na.action = na.omit)
grangertest(GDP_US_rt, RATE_rt, order = 1, na.action = na.omit)
grangertest(GDP_EU_rt_dif, RATE_rt, order = 1, na.action = na.omit)
grangertest(CPI_US_rt, RATE_rt, order = 1, na.action = na.omit)
grangertest(CPI_EU_rt, RATE_rt, order = 1, na.action = na.omit)
grangertest(XAU_USD_rt, RATE_rt, order = 1, na.action = na.omit)
grangertest(WTI_USD_rt, RATE_rt, order = 1, na.action = na.omit)
```
From the result, only GDP_EU_rt is significant, while it is a first order differential. So we tried cointegration test.

```{r}
currency.rate = as.numeric(RATE_rt)
#M1_US = as.numeric(M1_US_rt)
#M1_EU = as.numeric(M1_EU_rt)
#GDP_US = as.numeric(GDP_US_rt)
GDP_EU = as.numeric(GDP_EU_rt_dif)
#CPI_US = as.numeric(CPI_US_rt)
#CPI_EU = as.numeric(CPI_EU_rt)
#XAU_USD = as.numeric(XAU_USD_rt)
#WTI_USD = as.numeric(WTI_USD_rt)
```

```{r}
#md_lm = lm(currency.rate ~ M1_US + M1_EU + GDP_US + GDP_EU + CPI_US + CPI_EU + XAU_USD + WTI_USD)
md_lm = lm(currency.rate ~ GDP_EU_rt, data_rt_train)
summary(md_lm)
dwtest(md_lm)
res = residuals(md_lm)
ur.df(res, type = "none", selectlags = "AIC")
```

```{r}
x = cbind(GDP_EU_rt, RATE_rt)[1:50]
names(x) = c("GDP_EU", "RATE")
head(x)
```

```{r}
vecm = ca.jo(x, K = 2, ecdet = "const")
summary(vecm)
```
To construct the VAR model for the selected endogenous variables, the co-integration test is needed. Apply durbin-watson test to linear model. As the value of p-value is small enough, indicating that the residual sequence is not independent at the significance level of 5% and has autocorrelation. According to the stationariness test results of the residual series, the null hypothesis that the residual series has unit root is rejected at the significance level of 5%, that is, the residual series is stable, indicating that there is a co-integration relationship between currency rate and GDP of EU.  
From the result of Johansen procedure, we know the rank of the co-integration vector is 1.  
Then used cajorls() to estimate the coefficient matrix of the VEC model. Then VEC model is converted to horizontal VAR model to predict currency rate.
```{r}
md_vec = cajorls(vecm, r=1)
md_vec
md_var = vec2var(vecm, r = 1)
md_var
pred_var = predict(md_var, 12)
rmse(predicted = pred_var$fcst$RATE[1], actual = as.numeric(unlist(data_rt_test$RATE)))
#irf(md_var)
```

## DCC-GARCH

```{r}
#Calculate the maximum, minimum, median, skewness, kurtosis and extremum
data_outline = function(x){
  m = mean(x)
  d=max(x)
  xd=min(x)
  me = median(x)
  s = sd(x)
  kur=kurtosis(x)
  ske=skewness(x)
  R = max(x)-min(x)
  data.frame(Mean=m, Median=me, max=d,min=xd,std_dev=s, Skewness=ske, Kurtosis=kur, R=R)
}
for (i in  1:3){print(data_outline(data_D_rt[,i]))}
```

```{r}
ArchTest(M1_US1_rt)
ArchTest(CPI_US1_rt)
ArchTest(RATE1_rt)


ArchTest(XAU_USD1_rt)
ArchTest(WTI_USD1_rt)
ArchTest(RATE2_rt)
```
There is no ARCH effect of the monthly time series data, we decided to use the daily data, because ARCH effect shows in all three time series.

```{r}
#Calculate the correlation coefficient matrix
corre = cor(data_D_rt)
corre
```

```{r DCC-GARCH}
#1:   Conditional Mean (vs Realized Returns)
#2:   Conditional Sigma (vs Realized Absolute Returns)
#3:   Conditional Covariance
#4:   Conditional Correlation
#5:   EW Portfolio Plot with conditional density VaR limits
myuspec = multispec(replicate(3, ugarchspec(mean.model = list(armaOrder = c(1,1)))))
mydcc = dccspec(myuspec, VAR = TRUE, lag = 1, lag.max = 12, dccOrder = c(1, 1), distribution = 'mvnorm')
md_dcc = dccfit(mydcc, data = data_D_rt_train, fit.control = list(eval.se=TRUE))

myuspec1 = multispec(replicate(2, ugarchspec(mean.model = list(armaOrder = c(1,1)))))
mydcc1 = dccspec(myuspec1, VAR = TRUE, lag = 1, lag.max = 12, dccOrder = c(1, 1), distribution = 'mvnorm')
md_dcc_xau = dccfit(mydcc1, data = data_D_rt_train[, c(1, 3)], fit.control = list(eval.se=TRUE))
plot(md_dcc_xau)

md_dcc_wti = dccfit(mydcc1, data = data_D_rt_train[, c(2, 3)], fit.control = list(eval.se=TRUE))
plot(md_dcc_wti)
```

```{r}
#Predict with DCC-GARCH
pred_dcc = dccforecast(md_dcc, n.ahead = 14)
#pred_dcc
#fitted(pred_dcc)
rmse(predicted = as.numeric(unlist(fitted(pred_dcc)[3])), actual = as.numeric(unlist(data_D_rt_test[3])))
```

